### 2021-05-18 Supplementary_Material/Analysis_2_Hymenoptera_Families_Separated.Rmd
edits
Preparing supplementary material

---
output:
  pdf_document: default
  html_document: default
classoption: landscape

@@

#Plot nicely PC1
analysis_1 <- readRDS("results_analysis_1_bee_families.rds")
dat_analysis <- readRDS("dat_analysis_results_analysis_1_bee_families.rds")

@@

combined <- a1 + a2 + a3 & theme(legend.position = "right")
combined + plot_layout(guides = "collect", ncol=3)

```

>>>>

---
output:
  pdf_document: default
  html_document: default

@@

#Plot nicely PC1
analysis_1 <- readRDS("r_bee_families.rds")
dat_analysis <- readRDS("dat_bee_families.rds")

@@

combined <- a1 + a2 + a3 & theme(legend.position = "right")
combined_1 <- combined + plot_layout(guides = "collect", ncol=3)

saveRDS(combined_1, "Plot_bee_families.rds")

combined_2 <- readRDS("Plot_bee_families.rds")

combined_2
```
